---
title: "Shootings 2018"
output: html_document
---

```{r setup, include = FALSE}
library(knitr)
source("analysis.R")
```
### Summary Information
In the United States in 2018, there were `r num_shootings` shootings. 
These shootings killed a total of `r num_fatalities` people. The most impacted cities were: `r impact_statement`.
In total, `r total_fatality_rate`% of people who were shot were killed.

### State Information
By looking at each state, there appears to be a correlation between number of attacks and overall fatality rate of 
attacks. Additionally, Florida appears to be an outlier in the number of shootings, likely because it is the only state
which is required to release all police records, indicating missing information from other states. Lastly, there
is a correlation between both the number and deadliness of shootings and the latitudinal location of the state, indicating that 
southern states are more likely to have more and deadlier shootings.

```{r, echo = FALSE}
kable(state_summary, col.names = c("State", "Fatality Rate", "Killed", "Injured", "Shootings"))
```

### Specific Incident
In `r deadliest_attack$city` on `r deadliest_attack$date`, the deadliest attack of 2018 took place.
`r deadliest_attack$num_killed` person(s) were killed while `r deadliest_attack$num_injured` person(s) were injured.
This left a fatality rate of `r deadliest_attack$fatality_rate`%. For more information please refer to:
https://en.wikipedia.org/wiki/Mass_shootings_in_the_United_States

### Incident Map
Below is a visual representation of the locations of each of the shootings with indications of the severity. These representations clarify the grographical relationship
between the shooting locations and their severity. It may answer questions like: Are large shootings typically grouped together? Which states have more shootings than others?
```{r, echo=FALSE}
map_plot
```

### Severity Plot
The main question most people want answered is "How does state policy affect the 
severity of mass shootings?" Some believe that states where guns are more common
will have less severe shootings while others believe the exact opposite.
This plot analyzes the variance of the severity of the shootings in each state 
to clarify _if_ there is a significant effect from state policy
on shooting severity (indicated by a unique range in shootings) and _what_ that effect
is (indicated by a higher or lower mean).
```{r, fig_width = 1000, fig_length = 1000, echo=FALSE}
severity_plot
```






