---
title: "index"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
source("civic-info.R")
source("propublica.R")
```
####For my project, I analyzed those representing `r chosen_address` using the following:

1. https://projects.propublica.org/api-docs/congress-api/ 
2. https://developers.google.com/civic-information/

It is a _very cool_ project that I had **so much** fun spending my weekend on.


#####Here is some information on my local representatives
```{r, echo = FALSE}
kable(civic_data_frame)
```

## House of Representatives
Looking at **all** the congressional representatives (In the House, not the Senate)

This is how gender and party breakdown for those from the state of the address.
```{r, echo=FALSE}

party_plot

gender_plot
```


##`r individual_name`
Let's learn more about _`r individual_name`_. This person is `r age` years old,
and you can find them on twitter at `r twitter_account`. Interestingly, of the last
20 congressional votes, the representative was in accordance with the majority
`r success_percentage` of the time.

