---
title: "Assignment 7"
author: "Team BD5"
date: "May 8, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(dplyr)
source("./scripts/summary.R")
source("./scripts/chart1.R")
source("./scripts/chart2.R")
source("./scripts/chart3.R")
source("./scripts/chart4.R")
```

## Summary

From looking at the introduction survey data from everyone in the
course, we decided to showcase the class standings represented.
From the responses, there seems to be 
**`r intro_function(intro_survey)$freshman`** _freshman_,
**`r intro_function(intro_survey)$sophomore`** _sophomores_,
**`r intro_function(intro_survey)$junior`** _juniors_,
**`r intro_function(intro_survey)$senior`** _seniors_, 
and **`r intro_function(intro_survey)$blank`** person decided to leave it 
_blank_.

## Chart 1

```{r echo=FALSE}
chart_1(dataset_frame)
```

## Chart 2

```{r echo=FALSE}
chart_2(intro_survey)
```

## Chart 3

```{r echo=FALSE}
major_git_plot(intro_survey)
```

## Chart 4

```{r echo=FALSE}

```